Accessible and Usable Datasets yet Majority are Bronze-Graded and not Updated Regularly

### 2025-05-14 paper/paper.qmd
Updated paper

In the analysis of our paper, we looked at the following questions: What is the quality of the datasets on Open Data Toronto? What are the features of different types of datasets on Open Data Toronto?

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

>>>>

In the analysis of our paper, we looked at the following questions: What is the quality of the datasets on the Open Data Toronto portal? What are the features of different types of datasets on Open Data Toronto?

@@

Our variables of interest are "accessibility", "completeness", "freshness", "metadata", "usability", and "grade".
